---
title: "Ikea"
author: "Fanyi Zeng"
date: '2022-05-04'
output: github_document
---

```{r data, message = FALSE}
ikea <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-11-03/ikea.csv')
```

```{r pkg, message = FALSE}
library(tidymodels)
```

Let's take a look at the distribution of price. The distribution is right/positively skewed. Most items are in the lower price range.

```{r price}
ikea %>%
  ggplot(aes(x=price)) +
  geom_histogram()
```

They are selling a lot of desks, chairs, and shelves.

```{r category}
ikea %>%
  ggplot(aes(y=category)) +
  geom_histogram(stat="count")
```

Sofas, desks, chairs, wardrobes are the more expensive items.

```{r pricecat}
ikea %>%
  ggplot(aes(x=price,y=category)) +
  geom_bar(stat="identity")
```

Most items are sellable online, so there won't be much value in comparing the prices between online and on-site items.

```{r sell}
ikea %>%
  count(sellable_online)
```

On average, items that have other colors are more expensive (higher mean, median, and mode).

```{r pricecol}
ikea %>% 
  filter(other_colors=="Yes") %>%
  summary(price)
ikea %>% 
  filter(other_colors=="No") %>%
  summary(price)
```

Indeed, there seems to be a positive, significant relationship between item price and whether it has other colors.

```{r model}
m <- lm(price ~ other_colors, ikea)
summary(m)
```

In the lower price range, more items don't have colors. In the higher price range, more items have colors. 

```{r pricecol2}
ikea %>%
  ggplot(aes(y=price,fill=other_colors)) +
  geom_histogram(binwidth=500,position="fill")
```

Most colorful items: sofas, cabinets, room dividers, TV & media furniture. Least colorful items: trolleys, bar furniture, wardrobes.

```{r catcol}
ikea %>%
  ggplot(aes(y=category,fill=other_colors)) +
  geom_histogram(stat="count",position="fill")
```

Next time I shop at Ikea, I know where to look for those colorful items!

